Article 2:	Information-Seeking Behavior Decision-Making between Online Search and Interpersonal Networks: The Case of Covid-19 Vaccinations 

### 2022-01-24 paper2.Rmd
Add chi2 test

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, 
               # rms, 
               modelsummary, showtext, thematic, kableExtra, scales)

@@

@@

My analytic strategy proceeds in four steps. In Tables \@ref(tab:table-1-desc) 
& \@ref(tab:table-2-desc), I present descriptive statistics for all study 
variables, including variable ranges, means, and standard deviations. For this 
paper, I rely heavily on logistic regression, modeled in `r`; specifically, I 
fit a series of Binomial Generalized Linear Models [@venables2002a]. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r` [@modelsummary] ]
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information ('Received info') as well as various demographic variables such as
age, education level and race. Figure \@ref(fig:plot-model-1) then illustrates
the relationship between the coefficients and information seeking.^[Figures in this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
In Table \@ref(tab:table-model-2), I disaggregate information seeking behaviors
by modelling a series of logistic regressions that predict the 5 different
avenues of seeking information about Covid-19: from another person, from a
doctor, on an online forum, on a social networking site, or using an online
search tool.
Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then illustrates
the relationship between the coefficients and vaccination outlook.

@@

modelsummary(mod1,
            gof_omit = 'AIC', statistic = NULL,
            estimate = "{estimate}{stars} ({std.error})",
            title = 'What predicts someone intentionally searched for information',
            add_rows = rows,
            coef_map = regression_labels,
            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Exponentiated Coefficients'),         
            exponentiate = TRUE,
            output = "kableExtra") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

@@

## Information Search Vehicles
```{r table-model-2}
#| results = "asis"

@@

modelsummary(part2_models,
             align="llllll",
             statistic = NULL,
            estimate = "{estimate}{stars}",
            gof_omit = 'AIC',
            coef_map = regression_labels,
            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Exponentiated Coefficients'),            
            title = 'What predicts someone intentionally searched for information, by vehicle of information search',
            exponentiate = TRUE,
            add_rows = rows,
            output = "kableExtra") %>%
  kable_styling(latex_options = c("scale_down", "hold_position", "striped"))  %>%
  add_header_above(c(" " = 1, "Dependent Variable" = 5))
```

@@

@@

modelsummary(mod3,
            gof_omit = 'AIC', statistic = NULL,
            estimate = "{estimate}{stars} ({std.error})",
            title = 'Does receiving or searching for information predict vaccination status?',
            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Exponentiated Coefficients'),        
            coef_map = regression_labels,
            add_rows = rows,
            exponentiate = TRUE,
            output = "kableExtra") %>%
  kable_styling(latex_options = c("hold_position", "striped"))
```
Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 
`r round(exp(mod3$coefficients[['receive_i_fr_dr1']]), 2)` odds of receiving 
a Covid-19 vaccinated ( _p_ < 0.001) and that seeking information from a doctor
also increases the odds of vaccination by 
`r round(exp(mod3$coefficients[['int_sought_fr_dr1']]), 2)` ( _p_ < 0.001).
I find that my respondents who received information on a social networking site 
like Facebook or Twitter about the vaccines were 
`r label_percent()(1-round(exp(mod3$coefficients[['receive_i_fr_onlnet1']]), 2))` 
**less likely** to get vaccinated than those who received no information through
that vehicle ( _p_ < 0.001). However, I did find that those who reached out to
family or friends with their concerns were 
`r label_percent()(exp(mod3$coefficients[['int_sought_fr_pers1']])-1)` more likely
to become vaccinated ( _p_ < 0.05). Furthermore, my respondents who held an 
Associate's degree or above had `r round(exp(mod3$coefficients[['college1']]), 2)`
higher odds of becoming immunized ( _p_ < 0.001). And finally, I found further
ethno-racial differences in my sample. I found that Hispanic-Latinos had 
`r round(exp(mod3$coefficients[['hispanic1']]), 2)` higher odds of vaccination
than non-Hispanics ( _p_ < 0.05) and that my Asian sample had 
`r round(exp(mod3$coefficients[['race_asian1']]), 2)` higher odds as well over
non-Asians ( _p_ = 0.09). See Figure \@ref(fig:plot-model-3) for a visual 
representation of how these different coefficients are related to vaccination 
outlook. 
<!-- TODO: watch out about saying vaccinated, this variable is about opinion -->

@@

summary of purpose

for results - Table 1
this never before seen pattern in sociology may be a result of response bias, (most likely to select more information) but it also could indicate a sheltering effect ...

@@

Est velit egestas dui id ornare arcu odio ut. Tempus iaculis urna id volutpat
lacus laoreet non curabitur gravida. Integer malesuada nunc vel risus commodo.
Ipsum nunc aliquet bibendum enim facilisis gravida. Ac turpis egestas maecenas
pharetra convallis posuere morbi leo. Id diam vel quam elementum pulvinar etiam.
Neque aliquam vestibulum morbi blandit cursus risus at ultrices mi. Sem
fringilla ut morbi tincidunt augue interdum velit euismod. Ullamcorper eget
nulla facilisi etiam dignissim diam quis enim lobortis. Turpis egestas pretium
aenean pharetra magna ac placerat vestibulum lectus. Elit ut aliquam purus sit
amet luctus venenatis. Vitae tempus quam pellentesque nec nam. In est ante in
nibh. Nisl tincidunt eget nullam non nisi est sit. Cras adipiscing enim eu
turpis egestas. Velit dignissim sodales ut eu sem integer vitae justo eget. Arcu
non sodales neque sodales ut etiam sit amet. Turpis in eu mi bibendum neque
egestas congue quisque egestas.

At varius vel pharetra vel turpis nunc eget lorem. In nulla posuere sollicitudin
aliquam. Dui faucibus in ornare quam. Vivamus arcu felis bibendum ut tristique.
Ornare aenean euismod elementum nisi. Eget aliquet nibh praesent tristique.
Rhoncus dolor purus non enim praesent elementum. Id faucibus nisl tincidunt eget
nullam non nisi est. Eget arcu dictum varius duis at consectetur lorem donec
massa. At tempor commodo ullamcorper a lacus vestibulum sed arcu.

Lectus mauris ultrices eros in. Diam ut venenatis tellus in metus vulputate eu
scelerisque. Magna ac placerat vestibulum lectus mauris. Est velit egestas dui
id ornare arcu odio ut. Sagittis aliquam malesuada bibendum arcu vitae
elementum. Nisi lacus sed viverra tellus in hac habitasse. Nunc eget lorem dolor
sed. Condimentum id venenatis a condimentum vitae. Ipsum faucibus vitae aliquet
nec ullamcorper sit amet risus nullam. Tincidunt eget nullam non nisi est.
Ornare quam viverra orci sagittis eu volutpat. Risus quis varius quam quisque.
Lobortis scelerisque fermentum dui faucibus. A diam sollicitudin tempor id eu
nisl nunc mi ipsum.

\newpage
# References {-}

>>>>

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, 
               modelsummary, showtext, thematic, kableExtra, scales)

@@

# Abstract 
How do individuals perform information search, and what factors help them decide
which information search vehicle to utilize, such as interpersonal networks or
online tools, I investigate the above question  using individual survey data of
934 Adults in the United States and find that

Knowing that Google
trends data only encompasses a small portion of the information-seeking done by
modern humans, it is important to investigate what leads individuals to search
for a question online using a search engine versus more traditional means of
information gathering, such as network activation (asking someone in their
social network for informational support). I predict that few people will
activate their social network for informational support in my chosen case of
Covid-19 vaccinations because of the social cost of doing so and that the
majority will have utilized an online search engine.

@@

My analytic strategy proceeds in four steps. In Tables \@ref(tab:table-1-desc) 
& \@ref(tab:table-2-desc), I present descriptive statistics for all study 
variables, including variable ranges, means, and standard deviations. For this 
paper, I rely heavily on logistic regression, modeled in `r`; specifically, I 
fit a series of Binomial Generalized Linear Models [@venables2002a]. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r` [@modelsummary] ]
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information ('Received info') as well as various demographic variables such as
age, education level and race. Figure \@ref(fig:plot-model-1) then illustrates
the relationship between the coefficients and information seeking.^[Figures in this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
In Table \@ref(tab:table-model-2), I disaggregate information seeking behaviors
by investigating the difference in proportions of each of the vehicles in 
\@ref(tab:model-2-chi2) and then by modelling a series of logistic regressions 
that predict the 5 different avenues of seeking information about Covid-19: 
from another person, from a doctor, on an online forum, on a social networking 
site, or using an online search tool.
Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then illustrates
the relationship between the coefficients and vaccination outlook.

@@

modelsummary(mod1,
            gof_omit = 'AIC', statistic = NULL,
            estimate = "{estimate}{stars} ({std.error})",
            title = 'What predicts someone intentionally searched for information',
            add_rows = rows,
            coef_map = regression_labels,
            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Raw, Unexponentiated Coefficients'),            
            # exponentiate = TRUE,
            output = "kableExtra") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

@@

## Information Search Vehicles
```{r model-2-chi2}
#| results = "asis"

chi <- rain %>% 
  select(pers = int_sought_fr_pers,
         dr = int_sought_fr_dr,
         forum = int_sought_fr_onlgroup,
         net = int_sought_fr_onlnet,
         search = int_sought_fr_onlsearch)

find_p <- function(x, y){
  tab <- table(x, y)
  as.numeric(chisq.test(tab)["p.value"])
}

chi_squared_tests <- 
tribble(~col, ~Person, ~Dr, ~`Online Forum`, ~`Online Network`, ~`Online Search`,
'Person',   NA, find_p(chi$pers, chi$dr), find_p(chi$pers, chi$forum), find_p(chi$pers, chi$net), find_p(chi$pers, chi$search),
'Dr',     NA, NA, find_p(chi$dr, chi$forum), find_p(chi$dr, chi$net), find_p(chi$dr, chi$search),
'Online Forum',  NA, NA, NA, find_p(chi$forum, chi$net), find_p(chi$forum, chi$search),
'Online Network',    NA, NA,NA, NA, find_p(chi$net, chi$search),
'Online Search', NA, NA, NA, NA, NA)

chi_squared_tests %>%
  mutate(across(where(is.numeric), ~ sprintf("%.3f", round(., digits = 3)))) %>% 
  mutate(Person = cell_spec(Person, format = "html", bold = Person < 0.05),
       Dr = cell_spec(Dr, format = "html", bold = Dr < 0.05),
       `Online Forum` = cell_spec(`Online Forum`, format = "html", bold = `Online Forum` < 0.05),
       `Online Network` = cell_spec(`Online Network`, format = "html", bold = `Online Network` < 0.05),
       `Online Search` = cell_spec(`Online Search`, format = "html", bold = `Online Search` < 0.05)) %>% 
  kable(., escape = FALSE,
      digits=3,  
      caption = "Pearson's $\\chi^2$ test with Yates' continuity
	correction  between each Information Search Vehicle",
      col.names = c("",'Person', 'Dr', 'Online Forum', 'Online Network', 'Online Search')      ) %>% 
  kable_styling(latex_options = c("hold_position", "striped"),
                full_width = F) %>%
  column_spec(column = 1, bold = T) %>% 
  footnote(c("Bolded values are significant using $\\alpha = 0.05$, two-tailed test"))
```

```{r table-model-2}
#| results = "asis"

@@

modelsummary(part2_models,
             align="llllll",
             statistic = NULL,
            estimate = "{estimate}{stars}",
            gof_omit = 'AIC',
            coef_map = regression_labels,
            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Raw, Unexponentiated Coefficients'),            
            title = 'What predicts someone intentionally searched for information, by vehicle of information search',
            # exponentiate = TRUE,
            add_rows = rows,
            output = "kableExtra") %>%
  kable_styling(latex_options = c("scale_down", "hold_position", "striped"))  %>%
  add_header_above(c(" " = 1, "Dependent Variable" = 5))
```

@@

TODO interpret table \@ref(tab:model-2-chi2), the chi2 tests to see differences

@@

modelsummary(mod3,
            gof_omit = 'AIC', statistic = NULL,
            estimate = "{estimate}{stars} ({std.error})",
            title = 'Does receiving or searching for information predict vaccination status?',
            notes = list('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Raw, Unexponentiated Coefficients'),            
            coef_map = regression_labels,
            add_rows = rows,
            # exponentiate = TRUE,
            output = "kableExtra") %>%
  kable_styling(latex_options = c("hold_position", "striped"))
```
Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 
`r round(exp(mod3$coefficients[['receive_i_fr_dr1']]), 2)` odds of receiving 
a Covid-19 vaccinated ( _p_ < 0.001) and that seeking information from a doctor
also increases the odds of vaccination by 
`r round(exp(mod3$coefficients[['int_sought_fr_dr1']]), 2)` ( _p_ < 0.001).
I find that my respondents who received information on a social networking site 
like Facebook or Twitter about the vaccines were 
`r label_percent()(1-round(exp(mod3$coefficients[['receive_i_fr_onlnet1']]), 2))` 
**less likely** to get vaccinated than those who received no information through
that vehicle ( _p_ < 0.001). However, I did find that those who reached out to
family or friends with their concerns were 
`r label_percent()(exp(mod3$coefficients[['int_sought_fr_pers1']])-1)` more likely
to become vaccinated ( _p_ < 0.05). Furthermore, my respondents who held an 
Associate's degree or above had `r round(exp(mod3$coefficients[['college1']]), 2)`
higher odds of becoming immunized ( _p_ < 0.001). And finally, I found further
ethno-racial differences in my sample. I found that Hispanic-Latinos had 
`r round(exp(mod3$coefficients[['hispanic1']]), 2)` higher odds of vaccination
than non-Hispanics ( _p_ < 0.05) and that my Asian sample had 
`r round(exp(mod3$coefficients[['race_asian1']]), 2)` higher odds as well over
non-Asians ( _p_ = 0.09). See Figure \@ref(fig:plot-model-3) for a visual 
representation of how these different coefficients are related to vaccination 
outlook. 
<!-- TODO: watch out about saying vaccinated, this variable is about opinion -->

@@

summary of purpose of paper

We contribute to the literature by using a multivariable approach to identify
the sociodemographic factors associated with specific panethnic label
preferences among Latinos/Hispanics. Specifically, we focus on how U.S. region,
generation-since-immigration, racial identification, citizenship status,
language use, national origin, education, and political affiliation shape
panethnic label preference. We also call attention to factors associated with no
preference at all for these terms

table 1 and 2 main findings

- receive info from any source increases searching for information 
- older respondents more likely to search for information, perhaps indicating that 
they are less likely to trust initial sources and dig deeper, perhaps indicating less
polarization among older groups? 
- higher education more likely to seek out  more information, also seen in table 2
- blacks more likely to seek out more information
usage of different information search vehicles varies by demographics and also reception of different ifnromation
- overall, receiving information about Covid-19 vaccination generally spurs information seeking behaviors, though there are variations
- receive info from doctor leads to searching info from doctor, likely indicates good communication and trust in doctor, solid relationship with healthcare professionals
- few things predict seeking out information from another person, personal networks are so embedded in everyday life so perhaps don't remember doing it or behavioral prediction is notoriously hard
- Received Info, Social Networking Site negatively predicts Online Forum, indicating that if your social networks fulfill your need for information you don't need to extend out to online forums to ask for things, need is already met? 
- Asians are really unlikely to use online forums to find information in this context, very strong association but hispanics are more likely than non-hispanics to search online 
- online search is much less likely from those with higher education, which is counter intuitive since they are the population that has been the most trained in research methods and critical thinking .. perhaps they trust the information that they hear if they consider it to be a trusted source (typical higher education format of trust the professor) so they don't look deeper into it? basically already have high social capital in other ways, already set up to receive the information they needed and trusted
- older populations are more likely to 'just google it'

takeaways: Not everyone is activating their personal social networks or using Google in the same rates, the internal variation of users is important to consider when using something like Google Trends
education really affects information seeking behavior
ethno-racial differences affect information seeking behavior, more research should look into why there are group differences (likely cultural)

Takeaway 2: in person, online, or search engines?

table 3 main findings 
- very important for getting people to get vaccinated - a major goal for public Health authorities over the last two years
- extremely importnat given misinformation around vaccinations 
- receiving information from a doctor or other medical profession (or seeking) leads to more positive opinions. action inspired by this - difficult because of lack of primary care doctors for many americans, but every doctor should discuss the importance for every patient they interact with 
- receiving information from a social networking site NOT an online for results in less vaccinations. 
- differences in education level and race ; seen in prior literature however most current literature claims that anti-vacination attitudes span social class, political ideology, and X.

social netwokring site
info from doctor

<!-- this never before seen pattern in sociology may be a result of response bias, (most likely to select more information) but it also could indicate a sheltering effect ... <--- I wish I knew what I was talking about here -->

@@

Est velit egestas dui id ornare arcu odio ut. Tempus iaculis urna id volutpat
lacus laoreet non curabitur gravida. Integer malesuada nunc vel risus commodo.
Ipsum nunc aliquet bibendum enim facilisis gravida. Ac turpis egestas maecenas
pharetra convallis posuere morbi leo. Id diam vel quam elementum pulvinar etiam.

\newpage

# Conclusion

# References {-}
